---
title: "Gallery of Effects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Gallery of Effects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sparkler)
```

This gallery demonstrates the visual engines available in `sparkler`. These effects render using HTML5 Canvas.

## 1. Weather Effects (Atmosphere)

Use `sparkler::weather()` to create ambient backgrounds. By default in RMarkdown, these render in a contained box.

### Snow
```{r snow, echo=TRUE}
sparkler::weather(type = "snow", density = 2, height = "300px")
```

### Rain
```{r rain, echo=TRUE}
sparkler::weather(type = "rain", density = 1, speed = 0.8, height = "300px")
```

### Meteors
```{r meteor, echo=TRUE}
sparkler::weather(type = "meteor", density = 1, height = "300px")
```

## 2. Celebration Effects

These effects are typically triggered by events (like a button click in Shiny), but here we trigger them on page load.

### Confetti
```{r confetti, echo=TRUE}
# This creates a burst of confetti inside this box
sparkler::confetti(particle_count = 100, spread = 170)
```

### Fireworks
```{r fireworks, echo=TRUE}
# Fireworks run for a specific duration
sparkler::fireworks(duration = 10, speed = 1)
```
